Title

### 2018-08-31 thesis/paper/paper.tex
Improved require pattern

If qualifier non-existence should be tested the predicates have to be adapted, since they do not have a unique identifier. Their order has to be established using the entire set of statement ID, property and value. For this the predicates first\_qualifier\([3]\) and last\_qualifier\([3]\) taking the statement ID, the property and the value and next\_qualifier\([6]\) with ID, property and value for the current and next qualifier are introduced.\\

Using this pre-processed data the approach is to apply a require-predicate to each statement or qualifier. This is require\([3]\) for statements, connecting the statement ID with the constrained property \(p\) and the required term \(t\) and require\([5]\) taking the statement ID, property, and value of a qualifier and linking this with \(p\) and \(t\).\\

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, p, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(S, p, t) \leftarrow \text{next}(O, S) \wedge \text{require}(O, p, t) \wedge c
\end{equation*}
propagates this down the statement chain.

>>>>

If qualifier non-existence should be tested the predicates have to be adapted, since qualifiers do not have a unique identifier. To assign them a unique identity, statement ID, property and value have to be used. For this the predicates first\_qualifier\([3]\) and last\_qualifier\([3]\) taking the statement ID, the property and the value and next\_qualifier\([6]\) with ID, property and value for the current and next qualifier are introduced.\\

Using this pre-processed data, the approach is to apply a require-predicate to each statement or qualifier. This is require\([3]\) for statements, connecting the statement ID with the constrained property \(p\) and the required term \(t\) and require\([5]\) taking the statement ID, property, and value of a qualifier and linking this with \(p\) and \(t\).\\

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge \ldots \wedge C_m\) with atoms \(C_i\) depending on the constraint which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, p, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(S, p, t) \leftarrow \text{next}(O, S) \wedge \text{require}(O, p, t) \wedge c
\end{equation*}
propagates this down the statement chain.
